### 2012-06-21 inst/examples/Sethi.Rmd

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
orig = getOption("device")
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .1
sigma_m <- .1
sigma_i <- .1
````

@@

``` {r noise}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r  parallel}
require(snowfall) 
sfInit(parallel=TRUE, cpu=16)
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
````
Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.

@@

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

``` {r sethiplots}
policy <- data.frame(stock = x_grid, value = opt$D[,1])
ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value])) + 
	geom_smooth(aes(stock, stock-x_grid[value])) + ylab("escapement")

@@

``` {r  simulate }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

@@

``` {r  tidy}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "reps") # names are nice
````

@@

``` {r  p0}
p0 <- ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") 
p0
````

@@

``` {r  p1}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````

@@

``` {r biblio, echo=FALSE, results="asis"}
knitcitations::bibliography("html")
````

``` {r cleanup}
options(device=orig)
````

>>>>

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
op = options()
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
sigma_m <- .5
sigma_i <- .5
````

@@

``` {r noise, dependson="miscpars"}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
z_m <- function() 1+(2*runif(1, 0,  1)-1) * sigma_m
z_i <- function() 1+(2*runif(1, 0,  1)-1) * sigma_i
````

@@

``` {r  parallel, cache=FALSE}
require(snowfall) 
sfInit(parallel=TRUE, cpu=16)
````

``` {r sdp_mat, dependson="noise"}
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e5)
````
Note that `SDP_Mat` is specified from the calculation above, as are our grids and our profit function. `OptTime` is the stopping time.  `xT` specifies a boundary condition at the stopping time. A reward for meeting this boundary must be specified for it to make any difference.  `delta` indicates the economic discount rate. Again, details are in the function documentation.

@@

``` {r  find_dp_opt, dependson="sdp_mat" }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

``` {r sethiplots, dependson="find_dp_opt"}
policy <- data.frame(stock = x_grid, value = opt$D[,1])
ggplot(policy) + 
  geom_point(aes(stock, stock-x_grid[value])) + 
	geom_smooth(aes(stock, stock-x_grid[value])) + ylab("escapement")

@@

``` {r  simulate, dependson="find_dp_opt" }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

@@

``` {r  tidy, dependson="simulate"}
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "reps") # names are nice
````

@@

``` {r  p0, dependson="tidy"}
p0 <- ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") 
p0
````

@@

``` {r  p1, dependson="tidy"}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````

@@

``` {r biblio, echo=FALSE, results="asis"}
print(knitcitations::bibliography(), style="html")
````

``` {r reset, echo=FALSE, include=FALSE}
options(op)
````
